Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-11-29 SolEnRevision_3/solar_energy_rev1.tex
Final version for resubmission

STPV, ST, and TPV systems all share common surfaces but operate under
different conditions.  ST and STPV systems offer an alternative to PV
power generation in alternative energy systems.  Since both are heat
engines, they \textcolor{red}{are bounded by the Carnot limit and can
theoretically exhibit extremely high efficiencies under high (but attainable) operating conditions.}
\textcolor{black}{Additionally, since both ST and STPV systems rely on
elements heated to high temperatures via concentrated solar energy, they
are easy to modify for thermal storage of
energy~\cite{SteadyStateAnalysis,Night_time_Performance}.  This would
allow them to operate into the night.  An advantage of ST systems over
STPV systems is that ST systems do not require the use of PV cells.  The
PV cells in STPV systems are expensive and can limit overall system size.
Conversely, an advantage of STPV systems over ST systems is that STPV
systems have no thermal fluid or moving parts.  This leads to them being
more stable and compact solutions.  Overall, ST tends to lend itself to
large, immobile power installations while STPV is better suited for small
applications.  TPV systems operate on the same principle as STPV systems,
but rely on an external heat source instead of solar
energy~\cite{Prototype_TPV}.  This allows them to be used in energy
reclamation systems.}

While both ST and STPV systems are capable of
\textcolor{red}{efficiencies approaching 85\%}, only ST systems have yet been
realized with high real-world efficiency~\cite{RF_OptExp_2009, RKR_RenEnRev_2013, nnnNature}.  This is due primarily to the challenges
related to the extremely high temperature operation of STPV systems; it is
the view of the authors that this presents exciting opportunities for
researchers in materials science, nanophotonics, and engineering to devise
strategies for increasing the temperature stability of STPV components,
and for increasing the performance of STPV components operating at lower
temperature.  STPV systems have many advantages, such as those listed in
the previous paragraph, that make them attractive for further
development.

@@

\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} \textcolor{red}{Maximum theoretical efficiency for various STPV system temperatures.  This ideal limiting
efficiency can be computed from the product of a Carnot efficiency for the system 
with an absorber efficiency which accounts for the 
radiative losses that the system will experience as a function of temperature.  The fast increase
around typical operation temperatures of STPV systems (1000-2000 K) reflects the Carnot contribution, and the decline
starting at around 3000 K reflects the dominance of radiative losses at high temperatures.  See Ref.~\cite{me_thesis}
Chapter 4.1 for a detailed discussion of these limiting behaviors.}}
\end{center}
\end{figure}

@@

properties (the complex refractive index, \textcolor{red}{($\tilde{n} =

@@

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the \textcolor{red}{ultimate efficiency} of the emitter as a figure-of-merit,
where the \textcolor{red}{ultimate efficiency} depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with \textcolor{red}{ultimate efficiencies} of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with \textcolor{red}{ultimate efficiencies} of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with \textcolor{red}{ultimate efficiencies} of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the \textcolor{red}{ultimate efficiency} which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

\textcolor{red}{Because they operate at high temperatures, absorbing surfaces will lose energy through thermal emission.}  To reduce this loss, the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\epsilon_{abs}$ as the thermal emittance of an absorbing surface held at a specific temperature relative to the thermal emittance of a blackbody held at the same temperature.  This means that an absorbing surface with an $\epsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission of a blackbody at 1000$^\circ$C.  Note that the $\epsilon_{abs}$ of a surface can change drastically with temperature if its reflectivity and absorbance change for different wavelengths of light.  This is because the spectral composition of blackbody radiation changes with temperature.  At the same time, the solar absorptance ($\alpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

@@

\textcolor{red}{By transforming the incoming solar radiation from a
broad-band source to a more narrow-band one, STPV systems can operate at
efficiencies far exceeding the efficiency limit of 29\%
for single-junction silicon PV cells~\cite{scranton_from_gupta}, or the
higher limit of 40.8\% for a single-junction PV cell with an optimized
bandgap~\cite{opt_BG}.  This is due to the fact that the major factors
that limit efficiencies in these systems are losses due to below-bandgap
radiation and thermalization, which are both dependent on the spectrum of
light illuminating the PV cell~\cite{SQ}.  By efficiently altering the
spectrum of light reaching the PV cell, the system efficiency can be
increased.  In fact, the upper {\it theoretical} limit for STPV system
efficiency is 85.4\%~\cite{Therm_stabil_W_microstructures}.  While
reference \cite{RF_OptExp_2009} and \cite{global_opt} used many
idealities, they clearly show that STPV systems are capable of having
efficiencies above the 40.8\% limit for single junction PV cells.
Detailed balance calculations support this conclusion as well~\cite{g5}.}
\begin{table}
	\caption{\textcolor{red}{Absorber efficiency corresponding to equation \ref{overall_sss_eq}, relative solar absorption, and relative thermal emission. 
These data correspond to a temperature of 1700 K and a concentration factor of 2500 for selected absorbing surfaces.}}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{Palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

Table \ref{abs_eff_table} shows the $\alpha_{sol}$ and $\epsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface, \textcolor{red}{$C$ is the concentration factor of incoming sunlight, including concentrator ratio and concentrator efficiency,} $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their \textcolor{red}{ultimate efficiency} is used.

The \textcolor{red}{ultimate efficiency} is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
\eta = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the
bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon
with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral
emissivity of the emitting surface, approximated as the surface's
absorptivity.  This gives the relative efficiency of the
emitting surface, but does not represent an overall system efficiency.
Specifically, this equation does not take into account the fill factor,
open-circuit voltage, recombination losses within the PV cell, or any
non-idealities in the STPV system.  The values obtained from this equation
do not represent real or even potential system efficiencies, but serve as
a convenient way to compare the performance of various surfaces as well as
a tool for optimization.  While PV cells with external quantum
efficiencies that vary by wavelength could change the optimum bandgap
stated by this equation, the effect is generally small and would need to
be evaluated on a case by case basis.  \textcolor{red}{We note that typically, the emissivity of the emitter structure
will depend upon angle, and so the angular integration cannot simply be assumed to lead to a constant factor as suggested
by Eq. (5) above; see, for example, Ref.~\cite{RF_OptExp_2009} for a definition of the emitter efficiency that depends
explicitly upon emission angle.}

@@

\textcolor{black}{Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the \textcolor{red}{ultimate efficiencies} of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. These efficiencies are for systems operating under AM1.5 solar simulators or real-world solar conditions.  They all are converting solar energy to usable electrical energy (work).}

>>>>

STPV, ST, and TPV systems all share common surfaces but operate under
different conditions.  ST and STPV systems offer an alternative to PV
power generation in alternative energy systems.  Since both are heat
engines, they \textcolor{black}{are bounded by the Carnot limit and can
theoretically exhibit extremely high efficiencies under high (but attainable) operating conditions.}
\textcolor{black}{Additionally, since both ST and STPV systems rely on
elements heated to high temperatures via concentrated solar energy, they
are easy to modify for thermal storage of
energy~\cite{SteadyStateAnalysis,Night_time_Performance}.  This would
allow them to operate into the night.  An advantage of ST systems over
STPV systems is that ST systems do not require the use of PV cells.  The
PV cells in STPV systems are expensive and can limit overall system size.
Conversely, an advantage of STPV systems over ST systems is that STPV
systems have no thermal fluid or moving parts.  This leads to them being
more stable and compact solutions.  Overall, ST tends to lend itself to
large, immobile power installations while STPV is better suited for small
applications.  TPV systems operate on the same principle as STPV systems,
but rely on an external heat source instead of solar
energy~\cite{Prototype_TPV}.  This allows them to be used in energy
reclamation systems.}

While both ST and STPV systems are capable of
\textcolor{black}{efficiencies approaching 85\%}, only ST systems have yet been
realized with high real-world efficiency~\cite{RF_OptExp_2009, RKR_RenEnRev_2013, nnnNature}.  This is due primarily to the challenges
related to the extremely high temperature operation of STPV systems; it is
the view of the authors that this presents exciting opportunities for
researchers in materials science, nanophotonics, and engineering to devise
strategies for increasing the temperature stability of STPV components,
and for increasing the performance of STPV components operating at lower
temperature.  STPV systems have many advantages, such as those listed in
the previous paragraph, that make them attractive for further
development.

@@

\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} \textcolor{black}{Maximum theoretical efficiency for various STPV system temperatures.  This ideal limiting
efficiency can be computed from the product of a Carnot efficiency for the system 
with an absorber efficiency which accounts for the 
radiative losses that the system will experience as a function of temperature.  The fast increase
around typical operation temperatures of STPV systems (1000-2000 K) reflects the Carnot contribution, and the decline
starting at around 3000 K reflects the dominance of radiative losses at high temperatures.  See Ref.~\cite{me_thesis}
Chapter 4.1 for a detailed discussion of these limiting behaviors.}}
\end{center}
\end{figure}

@@

properties (the complex refractive index, \textcolor{black}{($\tilde{n} =

@@

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the \textcolor{black}{ultimate efficiency} of the emitter as a figure-of-merit,
where the \textcolor{black}{ultimate efficiency} depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with \textcolor{black}{ultimate efficiencies} of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with \textcolor{black}{ultimate efficiencies} of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with \textcolor{black}{ultimate efficiencies} of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the \textcolor{black}{ultimate efficiency} which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

\textcolor{black}{Because they operate at high temperatures, absorbing surfaces will lose energy through thermal emission.}  To reduce this loss, the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\epsilon_{abs}$ as the thermal emittance of an absorbing surface held at a specific temperature relative to the thermal emittance of a blackbody held at the same temperature.  This means that an absorbing surface with an $\epsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission of a blackbody at 1000$^\circ$C.  Note that the $\epsilon_{abs}$ of a surface can change drastically with temperature if its reflectivity and absorbance change for different wavelengths of light.  This is because the spectral composition of blackbody radiation changes with temperature.  At the same time, the solar absorptance ($\alpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

@@

\textcolor{black}{By transforming the incoming solar radiation from a
broad-band source to a more narrow-band one, STPV systems can operate at
efficiencies far exceeding the efficiency limit of 29\%
for single-junction silicon PV cells~\cite{scranton_from_gupta}, or the
higher limit of 40.8\% for a single-junction PV cell with an optimized
bandgap~\cite{opt_BG}.  This is due to the fact that the major factors
that limit efficiencies in these systems are losses due to below-bandgap
radiation and thermalization, which are both dependent on the spectrum of
light illuminating the PV cell~\cite{SQ}.  By efficiently altering the
spectrum of light reaching the PV cell, the system efficiency can be
increased.  In fact, the upper {\it theoretical} limit for STPV system
efficiency is 85.4\%~\cite{Therm_stabil_W_microstructures}.  While
reference \cite{RF_OptExp_2009} and \cite{global_opt} used many
idealities, they clearly show that STPV systems are capable of having
efficiencies above the 40.8\% limit for single junction PV cells.
Detailed balance calculations support this conclusion as well~\cite{g5}.}
\begin{table}
	\caption{\textcolor{black}{Absorber efficiency corresponding to equation \ref{overall_sss_eq}, relative solar absorption, and relative thermal emission. 
These data correspond to a temperature of 1700 K and a concentration factor of 2500 for selected absorbing surfaces.}}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{Palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

Table \ref{abs_eff_table} shows the $\alpha_{sol}$ and $\epsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface, \textcolor{black}{$C$ is the concentration factor of incoming sunlight, including concentrator ratio and concentrator efficiency,} $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their \textcolor{black}{ultimate efficiency} is used.

The \textcolor{black}{ultimate efficiency} is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
\eta = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the
bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon
with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral
emissivity of the emitting surface, approximated as the surface's
absorptivity.  This gives the relative efficiency of the
emitting surface, but does not represent an overall system efficiency.
Specifically, this equation does not take into account the fill factor,
open-circuit voltage, recombination losses within the PV cell, or any
non-idealities in the STPV system.  The values obtained from this equation
do not represent real or even potential system efficiencies, but serve as
a convenient way to compare the performance of various surfaces as well as
a tool for optimization.  While PV cells with external quantum
efficiencies that vary by wavelength could change the optimum bandgap
stated by this equation, the effect is generally small and would need to
be evaluated on a case by case basis.  \textcolor{black}{We note that typically, the emissivity of the emitter structure
will depend upon angle, and so the angular integration cannot simply be assumed to lead to a constant factor as suggested
by Eq. (5) above; see, for example, Ref.~\cite{RF_OptExp_2009} for a definition of the emitter efficiency that depends
explicitly upon emission angle.}

@@

\textcolor{black}{Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the \textcolor{black}{ultimate efficiencies} of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. These efficiencies are for systems operating under AM1.5 solar simulators or real-world solar conditions.  They all are converting solar energy to usable electrical energy (work).}

The simulations outlined here show a large difference in predicted efficiency; however, a significant portion of this variation is caused by simulation parameters.  Since there is no standard for simulated STPV systems, some papers use an ideal model where only losses due to the surfaces are accounted for, while others use a more realistic model that encompasses many losses.  Namely, references \cite{RF_OptExp_2009} and \cite{global_opt} assume ideal PV cells, ideal solar concentrators, and assume an ideal view-factor between the emitting surface and solar cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} attempt to model PV cell losses and realistic absorbing and emitting surfaces.  Some of the remaining difference between efficiencies in the modeled systems is also due to differences in assumptions between simulations.  \textcolor{black}{Additional technical challenges associated with STPV and TPV systems that are not included in any of the aforementioned studies include the high resistance losses associated with large current outputs form PV cells, and the large amount of cooling necessary to hold the PV cells at adequate temperatures.  While the use of selective emitters does significantly reduce the thermal load on the PV cells, active cooling will still be necessary for systems which utilize a high level of solar concentration.  The power required for this cooling is not taken into account in the efficiency numbers outlined in this review.}
